HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-08-06 scnn.tex
moved plots around so they are nicely positioned
updated figures, not sure if they are a lot better though

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{gaussian_filters_spectral}
\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}
\includegraphics[width=\linewidth]{gaussian_filters_section}
\caption{Three different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.
Top: graph spectral domain.
Middle: gnomonic projection.
Bottom: section plot.}
\label{fig:gaussian_filters_visualization}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{gaussian_filters_spectral}
\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$ in spectral domain.}
\vspace{0.3in}
\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}
\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$: cross-section of the kernel through the pixels along the equator.}
\vspace{0.3in}
\includegraphics[width=\linewidth]{gaussian_filters_section}
\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$ in a gnomonic projection.}
\label{fig:gaussian_filters_visualization}
\end{figure}

@@
